Red Oak: Proactive Policy Generation

### 2015-05-09 draft.tex
opt

@@

   % 2) Prune dead subtree on empty ranges and add/remove which do not affect any inhabitant-based branching.

>>>>

% Prune dead subtree on empty ranges and add/remove which do not affect any inhabitant-based branching.

@@

Other optimizations may further reduce the number of packet sent to the controller. For example, we could remove \lstinline|add| node which are followed by \lstinline|remove| node for the same relation and tuple on all path without the change being observed by an \lstinline|in_rel| node. Similarly, we could detect and warn the user if an added tuple may never be observed by an \lstinline|in_rel| node, for example by switching \lstinline|ipsrc| and \lstinline|ipdst| in the add tuple of the stateful firewall example (see Figure~\ref{fig:firewallcode}). We leave the implementation of these optimizations as future work.
